---
title: "BTV virus in Ecuador"
author: "Alfredo Acosta"
date: "2025-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries
```{r libraries}
library(terra)   # Replaces raster
library(sf)      # Replaces rgdal and rgeos
library(dplyr)
library(ggplot2)
library(ggspatial)  # Replaces ggsn
library(ggmap)
library(plotly)
library(sp)
library(geodata)
```

# Set Working Directory
```{r setwd}
setwd("C:/Users/alfredo.acosta/Papers/2023/BTV/V4.3.2/")
```

# Load WorldClim Data
```{r worldclim}
r <- geodata::worldclim_global(var = "bio", res = 2.5,
                               path = "./worldclim_data")
r <- r[[c(1, 4, 5, 6, 8, 9, 12, 13, 14, 15, 18, 19)]]
names(r) <- c("Temp", "tseason", "max", "min", "twettest", "tdriest",
              "Prec", "pwettest", "pdriest", "pseason", "pwarm", "pcold")
plot(r)
```
# Import Shapefile, Transform CRS, exclude galapagos
```{r shapefile}
# Read the shapefile
# Define the relative path to the shapefile
shapefile_path <- file.path(getwd(), "nxparroquias.shp")
ec3 <- st_read(shapefile_path)

# Check for invalid geometries
invalid_geometries <- st_is_valid(ec3, reason = TRUE)
table(invalid_geometries)

# Fix invalid geometries
ec3 <- st_make_valid(ec3)

# Re-check for validity
table(st_is_valid(ec3))

# exclude galapagos
ec3 <- ec3 %>% filter(DPA_DESPRO != "GALAPAGOS")
ec3 <- st_transform(ec3, crs = 4326)

```
# Compute Centroids and Extract Climate Data
```{r centroids}
trueCentroids <- st_centroid(ec3)
values <- terra::extract(r, vect(trueCentroids))
df <- cbind(st_coordinates(trueCentroids), values)
ec3 <- cbind(ec3, df)
```

# Plot Locations
```{r plot-map}
ggplot() +
  geom_sf(data = ec3, fill = "white", color = "black", linewidth = 0.01) +
  geom_point(data = df, aes(x = X, y = Y), color = "red", size = 0.5) +
  annotation_scale(location = "bl", width_hint = 0.2) +
  annotation_north_arrow(location = "lr", which_north = "true",
                         pad_x = unit(0.75, "in"), pad_y = unit(0.75, "in"),
                         style = north_arrow_fancy_orienteering) +
  theme_minimal()
```
# Create a Layer of Spatial Points
```{r spatial-points}
# Extract bio data to spatial points
values <- terra::extract(r, vect(trueCentroids))
df <- cbind(st_coordinates(trueCentroids), values)

# Merge extracted centroids data with shapefile
ec3 <- cbind(ec3, df[, c(1, 2)])
```

# Visualizing Ecuador Data
```{r plot-ecuador}
plot(r, xlim = c(-82, -75), ylim = c(-6, 2))
datos <- as.data.frame(ec3)
```

# Load and Process Outbreak Data
```{r outbreak-data}
c <- read.csv("Coordinates.csv")
d <- read.csv("Coordinates.Wahis.csv")
e <- read.csv("manabi.lon.lat.csv")
f <- read.csv("BTV_lat_long.csv")
f <- filter(f, definitivo == "caso")

# Standardizing column names
colnames(c)[1] <- "id"
colnames(e)[2] <- "id"
colnames(e)[5:8] <- c("X", "Y", "x", "y")
colnames(f)[c(2, 49, 48)] <- c("id", "x", "y")
d$id <- as.character(d$id)
e$id <- as.character(e$id)
f$id <- as.character(f$id)

# Combine all points
points <- bind_rows(
  c, d[, c(1, 5, 6)], e[, c(2, 7, 8)], f[, c(2, 49, 48)]
)
```

# Visualizing Outbreak Locations
```{r plot-outbreaks}
ggplotly(
  ggplot() +
    geom_point(data = points, aes(x = x, y = y, label = rownames(points))) +
    geom_label()
)
```

# Checking and Cleaning Data
```{r clean-data}
# Checking for duplicates
table(c$x %in% f$x)

# Removing NA values from points dataset
points <- filter(points, !is.na(x), !is.na(y))
```

# Maps
```{r}
# Import the base map of ecuador ---
# Download map looking at the bordes of colombia and Peru
# API registration
register_stadiamaps(key = "76b5ee9f-672a-4475-95ac-c3e2cbfbb72a")

ecu2 <- ggmap::get_stadiamap(bbox = c(left = - 81.4, 
                                     bottom = -5.1, 
                                     right = -75, 
                                     top = 1.6),
                             zoom = 8,
                             maptype = "stamen_terrain_background")

# import Quito limits
uio <- st_read(dsn = "C:/Users/alfredo.acosta/Papers/2023/BTV/V4.3.2/quito.shp")
uio <- st_transform(uio, crs = 4326)

# import GYE limits
gye <- st_read("C:/Users/alfredo.acosta/Papers/2023/BTV/V4.3.2/guayaquil.shp")
gye <- st_transform(gye, crs = 4326)

# convert base map to a raster layer
ecu2_raster <- as.raster(ecu2)
```

# Locating the outbreaks in the parish
```{r}
# Create the spatial points
sp <- SpatialPoints(points[, c(2, 3)])

# Use the entire map to intersect the points and polygons
ec3_sf <- st_as_sf(ec3)
sp_sf <- st_as_sf(sp)

ec3_sf <- st_transform(ec3_sf, crs = 4326)
sp_sf <- st_set_crs(sp_sf, 4326)

# Count the number of points within each polygon
ec3_sf$inter2 <- lengths(st_intersects(ec3_sf, sp_sf))
table(ec3_sf$inter2)

# Replace zeros with NA
ec3_sf <- ec3_sf %>%
  mutate(inter2 = ifelse(inter2 == 0, NA, inter2))

# Which are in False 153, True 887, now there is true 879
table(is.na(ec3_sf$inter2)) 

# Replace zeros with NA
ec3_sf <- ec3_sf %>%
  mutate(inter = ifelse(is.na(inter2), 0, 1))

# Which are in False 153, True 887, now there is true 879
table(ec3_sf$inter)
```

# Locations of outbreaks and number of outbreaks in areas on the map ----
```{r}
ggplot() +
  geom_sf(data = ec3_sf, aes(fill = inter2)) +
  geom_point(data = points, aes(x = x, y = y), size = 1, shape = 21, fill = "orange", color = "black") +
  scale_fill_viridis_c(direction = 1, option = "D", na.value = "gray90") +
  theme(strip.background = element_blank(), title = NULL)
```
# Temperature and precitipation descriptive analysis ----
```{r}
# Parishes with bluetongue Max temp 20.62
summary(ec3_sf$Temp[!is.na(ec3_sf$inter)])

boxplot(ec3_sf$Temp[!is.na(ec3_sf$inter)])

ec3_sf$bt <- ec3_sf$inter

as.data.frame(ec3_sf) %>% 
  group_by(bt) %>%
  summarise(mean_temp = mean(Temp),
            mean_prec = mean(Prec))
```
# Filtering optimal temperature ----
```{r}
ec3_sf <- ec3_sf %>% 
  mutate(opt = ifelse(min >12, 1, 0)) %>%
  mutate(opt2 = ifelse(max <32, 1, 0)) %>%
  mutate(opt3 = opt+opt2) %>%
  mutate(opt3 = ifelse(opt3 == 2, Temp, NA))

# Calculating the area
ec3_sf$area <- st_area(ec3_sf) / 1000000
sum(ec3_sf$area[!is.na(ec3_sf$opt3)]) / sum(ec3_sf$area, na.rm = TRUE)


# Area with ideal temperature
sum(ec3_sf$area) * 0.73

# How many parishes have the ideal conditions for Cullicoides spp?
table(!is.na(ec3_sf$opt3))
561 / 1040
#  54% of the territory
```


# Simulating rising in temperatures of 2.7 degrees ----
```{r}
# Filtering optimal temperature ----
ec3_sf_rising <- ec3_sf %>%
  mutate(opt = ifelse((min + 2.7) > 12, 1, 0)) %>%
  mutate(opt2 = ifelse((max) < 32, 1, 0)) %>%
  mutate(opt4 = opt + opt2) %>%
  mutate(opt4 = ifelse(opt4 == 2, (Temp + 2.7), NA))

# Calculating the area
ec3_sf_rising$area <- st_area(ec3_sf_rising) /1000000
sum(ec3_sf_rising$area[!is.na(ec3_sf_rising$opt3)])/sum(ec3_sf_rising$area, na.rm = TRUE)

# Area with ideal temperature # 248843.6 [m^2]
sum(ec3_sf_rising$area)*0.74

sum(ec3_sf_rising$area[!is.na(ec3_sf_rising$opt4)]) -
  sum(ec3_sf$area[!is.na(ec3_sf$opt3)])

# How many parishes have the ideal conditions for Cullicoides spp?
table(!is.na(ec3_sf_rising$opt4))
639 / 1040
639 - 561
```
# Identify the new parishes with ideal conditions in the example of rising temperature 2.7 degrees
```{r}
# Identifying the new parishes at rising
ec3_sf_rising <- ec3_sf_rising %>%
  mutate(rising = ifelse(is.na(opt3) & !is.na(opt4), opt4, NA))
table(is.na(ec3_sf_rising$rising))
# 957-1032 = 75 new
# New area
#  72% of the parish
```

# SM4 new added parishes with the 
```{r}
SM4 <- ggplot()+
  geom_sf(data = ec3_sf_rising, aes(fill = rising), linewidth = 0.00001) +
  scale_fill_viridis_c(direction = 1, option =  "D", na.value = "white") +
  theme(strip.background = element_blank(), title = NULL) +
  labs(fill = "+2.7 °C rise\nNew parishes\nScenario",
  x = NULL,
  y = NULL) +
  xlim(-81.1,- 75.1) +
  theme(text = element_text(size = 10),
        panel.spacing = unit(-0.5, "cm")) +
  theme(legend.key.width = unit(0.15, "cm"),
        legend.title = element_text(size = 8)) +
  theme_minimal() +
  ggsn::north(ec3_sf, symbol = 3) +
  ggsn::scalebar(ec3_sf, dist = 100, dist_unit = "km", transform = TRUE,
                 model = "WGS84", st.size = 2, st.dist = 0.05,
                 anchor = c(x = -76, y = -4.5),
                 height = 0.02, border.size = 0.09)

tiff(filename = "SM4.tiff", width = 13, height = 10,
     units = "cm", res = 1200, compression = "lzw", pointsize = 12)
SM4
dev.off()
```

# Reading cattle population and organizing population
```{r}
library(readr)# Reading cattle population ----
pop <- readxl::read_xlsx("AFTOSA_FASE_2023_EC.xlsx", sheet = "AFTOSA_FASE_2023_EC")
colnames(pop)
```

# Transforming Data to spatial visualization (Passing the map)
```{r readr}
vigi <- pop %>% 
  group_by(provincia, canton, parroquia) %>%
  summarize(cantidad = sum(as.numeric(total_aplicado), na.rm = TRUE))

sum(vigi$cantidad, na.rm = TRUE) #4656389

source("C:\\Users\\alfredo.acosta\\Papers\\2023\\BTV\\V4.3.2\\passthemap_sizse.update.R")  

# After passing the map the ec3 map is replaced withouth the previous information
sum(vigi$cantidad, na.rm = TRUE) #4656389
sum(ec3$cantidad, na.rm = TRUE) #4656389

# transfer number of animals to sf object
ec3_sf$pop <- ec3$cantidad[match(ec3_sf$DPA_PARROQ, ec3$DPA_PARROQ)]
sum(ec3_sf$pop, na.rm = TRUE) #105368 animals lacking

# Calculate density
ec3_sf$popden <- ec3_sf$pop / as.numeric(ec3_sf$area)
summary(ec3_sf$popden)
```

# Fig. 2A Mean temperature 
```{r}
# Create the plot
mA <- ggplot() +
  annotation_raster(ecu2_raster,
                    xmin = -81.4, xmax = -75, ymin = -5.1, ymax = 1.6) +
  geom_sf(data = ec3_sf, aes(fill = Temp), linewidth = 0.0000001) +
  scale_fill_viridis_c(direction = 1, option = "D", na.value = "gray90") +
  theme_minimal(base_size = 6)+
  theme(title = NULL,
        legend.key.width = unit(0.25, 'cm')) +
  labs(fill = "Average\nTemp.\n°C",
    x = NULL,
    y = NULL) +
  xlim(-81.1, -75.1) +
  geom_text(aes(x = -76, y = 1), label = "Colombia",
    size = 3, colour = "black") +
  geom_text(aes(x = -76, y = -3.5), label = "Peru",
    size = 3, colour = "black") +
  geom_sf(data = uio, aes(geometry = geometry), size = 0.1, alpha = 0.2, colour = "red") +
  geom_sf(data = gye, aes(geometry = geometry), size = 0.1, alpha = 0.2, colour = "red") +
  annotate("text", label = "Quito", x = -78.75, y = -0.06, size = 1.8, colour = "black") +
  annotate("text", label = "Guayaquil", x = -80.40, y = -2.0, size = 1.8, colour = "black") +
  ggsn::scalebar(ec3, dist = 100, dist_unit = "km", transform = TRUE,
    model = "WGS84", st.size = 2, st.dist = 0.05,
    anchor = c(x = -76, y = -4.5),
    height = 0.02, border.size = 0.09)

tiff(filename = "A.tiff", width=13, height=10,
     units="cm", res=1200,compression = "lzw", pointsize = 12)
mA
dev.off()
```
# Fig. 2B Map of optimal temperatures 
```{r}
mB <- ggplot()+
  geom_sf(data=ec3_sf, aes(fill=opt3), linewidth = 0.0000001) +
  scale_fill_viridis_c(direction = 1, option =  "D", na.value = "gray90")+
  theme_minimal(base_size = 6)+
  theme(title = NULL,
    legend.key.width = unit(0.25, 'cm')) +
  labs(fill =("Vector\nOptimal\nTemp.\n°C"),
    x=NULL,
    y=NULL) +
  xlim(-81.1 , -75.1) +
  ggsn::north(ec3_sf, symbol = 3) +
  ggsn::scalebar(ec3_sf, dist = 100, dist_unit = "km",transform = TRUE,
    model = "WGS84", st.size = 2, st.dist = 0.05,
    anchor = c(x = -76, y = -4.5),
    height = 0.02, border.size = 0.09)
  
tiff(filename = "B.tiff", width=13, height=10,
     units="cm", res=1200,compression = "lzw", pointsize = 12)
mB
dev.off()
```

# Fig. 2C Precipitation map ----
```{r}
mC <- ggplot()+
  geom_sf(data=ec3_sf, aes(geometry = geometry),
    colour = "black", linewidth = 0.0000001) +
  geom_sf(data=ec3_sf, aes(fill=Prec), linewidth = 0.0000001) +
  scale_fill_viridis_c(direction = 1, option =  "D", na.value = "gray90")+
  theme_minimal(base_size = 6)+
  theme(title = NULL,
    legend.key.width = unit(0.25, 'cm'))+
  labs(fill = "Annual\nPrecip.\nmm",
    x=NULL,
    y=NULL) +  
  xlim(-81.1,-75.1)+
  ggsn::north(ec3_sf, symbol = 3) +
  ggsn::scalebar(ec3_sf, dist = 100, dist_unit = "km",transform = TRUE,
    model = "WGS84", st.size = 2, st.dist = 0.05,
    anchor = c(x = -76, y = -4.5),
    height = 0.02, border.size = 0.09)

tiff(filename = "C.tiff", width=13, height=10,
     units="cm", res=1200, compression = "lzw", pointsize = 12)
mC
dev.off()
```

# Fig. 2D pp Graphic population and pop densities ----
```{r setwd}
mD <- ggplot()+
  geom_sf(data=ec3_sf, aes(fill=pop), linewidth = 0.0000001) +
  scale_fill_viridis_c(direction = -1, option = "D", na.value = "gray90")+
  theme_minimal(base_size = 6)+
  theme(title = NULL,
        legend.key.width = unit(0.25, 'cm'))+
  labs(fill=("Cattle\nPop\n(Animals)"),
       x=NULL,
       y=NULL) +
  xlim(-81.1,-75.1)+
  ggsn::north(ec3_sf, symbol = 3) +
  ggsn::scalebar(ec3_sf, dist = 100, dist_unit = "km",transform = TRUE,
                 model = "WGS84", st.size = 2, st.dist = 0.05,
                 anchor = c(x = -76, y = -4.5),
                 height = 0.02, border.size = 0.09)

tiff(filename = "D.tiff", width=13, height=10,
     units="cm", res=1200,compression = "lzw", pointsize = 12)
mD
dev.off()
```

# Fig 2 Creating composite map 4 maps in 1 ----
```{r setwd}
tiff(filename = "Fig21.tiff",
  width=18, height=13, units="cm", res=1200,
  compression = "lzw", pointsize = 12)

ggpubr::ggarrange(mA, mB, mC, mD, ncol = 2, nrow = 2, common.legend = FALSE, 
  labels = c("A", "B", "C", "D"), 
  font.label = list(size = 10, color = "black"))

dev.off()
```

# Density map
```{r setwd}
pd <- ggplot() +
  geom_sf(data = ec3_sf, aes(fill = popden)) +
  scale_fill_viridis_c(direction = -1, option = "D", na.value = "gray90") +
  theme_minimal(base_size = 10) +
  theme(title = NULL, legend.key.width = unit(0.25, 'cm')) +
  labs(fill = "Cattle\npop density", x = NULL, y = NULL) +
  xlim(-81.1, -75.1) +
  ggsn::north(ec3_sf, symbol = 3) +
  ggsn::scalebar(ec3_sf, dist = 100, dist_unit = "km", 
  transform = TRUE, model = "WGS84", st.size = 2, 
  st.dist = 0.05, anchor = c(x = -76, y = -4.5), height = 0.02, border.size = 0.09) +
  geom_point(data = points, aes(x = x, y = y), size = 0.02, color = "red", alpha = 0.7)

tiff(filename = "density.tiff", width=13, height=10,
     units="cm", res=1200,compression = "lzw", pointsize = 12)
pd
dev.off()
```

```{r setwd}
# Analyzing densitites
summary(ec3_sf$pop)
# Min.  1st Qu.   Median     Mean  3rd Qu.     Max.     NA's 

summary(ec3_sf$popden)
# Min.  1st Qu.   Median     Mean  3rd Qu.     Max.     NA's 
```


```{r setwd}
popdb <- ec3_sf %>% 
  group_by(DPA_DESPRO) %>% 
  summarize(p=sum(pop, na.rm = TRUE), 
                  t=mean(min, na.rm = TRUE))%>% 
  arrange(desc(p))

popdendb <- ec3@data %>% 
  group_by(DPA_DESPRO) %>% 
  summarize(d=mean(popden, na.rm = TRUE)) %>% 
  arrange(desc(d))

popdb$density <- popdendb$d
popdb <- popdb[,c(1,2,4,3)]

write.csv(popdb, file = "population-density-province.csv")
```

# 4 Read no cases of BTV from passive surveillance only
```{r}
nbtv <- read.csv("nobtv.csv")
colnames(nbtv)
sum(nbtv$value)

length(unique(nbtv$parroquia))

vigi <- nbtv %>%
  group_by(provincia, canton=cantón, parroquia) %>%
  summarise(cantidad = sum(value))

sum(vigi$cantidad , na.rm = TRUE)#4634
### Mapa FINAL

# Using a source function to realocate information provincia cantón y parroquia
source("C:\\Users\\alfredo.acosta\\Papers\\2023\\BTV\\V4.3.2\\passthemap_sizse.update.R")  

ec3_sf$sn <- ec3$cantidad[match(ec3_sf$ID, ec3_sf$ID)]
sum(ec3_sf$sn, na.rm = TRUE) #4634 #4355
```

# Read province map
```{r setwd}
shapefile_path <- file.path(getwd(), "nxprovincias.shp")
ec2 <- st_read(shapefile_path)

# Check for invalid geometries
invalid_geometries <- st_is_valid(ec2, reason = TRUE)
table(invalid_geometries)

# Fix invalid geometries
ec2 <- st_make_valid(ec2)

# Re-check for validity
table(st_is_valid(ec2))

# exclude galapagos
ec2 <- ec2 %>% filter(DPA_DESPRO != "GALAPAGOS")
ec2 <- st_transform(ec2, crs = 4326)

```
# Compute Centroids and Extract Climate Data
```{r centroids}
trueCentroids <- st_centroid(ec2)
ec2$x <- st_coordinates(trueCentroids)[,1]
ec2$y <- st_coordinates(trueCentroids)[,2]  

# Fig. 1 sn Graphic population and pop densities ----
sn <- ggplot() +
  geom_sf(data = ec3_sf, aes(fill = sn), linewidth = 0.00001) +
  scale_fill_viridis_c(direction = -1, option = "D", na.value = "gray90") +
  theme_minimal(base_size = 6) +
  theme(title = NULL,
        legend.key.width = unit(0.25, 'cm'))+
  labs(fill=("N°\nFarms\nUnder\nSurv."),
       x=NULL,
       y=NULL) +
  xlim(-81.1,-75.1)+
  geom_sf(data = ec2, fill = NA, colour = "black", linewidth = 0.1) +
  ggsn::scalebar(ec3_sf, dist = 100, dist_unit = "km", 
                 transform = TRUE, model = "WGS84", st.size = 2, 
                 st.dist = 0.05, anchor = c(x = -76, y = -4.5), height = 0.02, border.size = 0.09) +
  ggsn::north(ec2, symbol = 3) +
  geom_point(data = points, aes(x = x, y = y, colour = "BTV +"), size = 0.08, alpha = 0.7) +
  geom_point(data = c, aes(x = x, y = y, colour = "BTV +"), size = 0.08, alpha = 0.7) +
  geom_text(data = ec2, aes(x = x, y = y, label = DPA_PROVIN), size = 2)

tiff(filename = "Fig1.tiff", width = 11.5, height = 10,
     units = "cm", res = 2400, compression = "lzw", pointsize = 12)
sn
dev.off()

```

# Logistic model
```{r setwd}
library(stats)
library(epiDisplay)
library(ResourceSelection)
library(modEvA)
library(PerformanceAnalytics)

d <- data.frame(ec3_sf)
colnames(d)
str(d)

# 0 Dependent variable Case ----
d$fcaso <- factor(d$inter)

table(d$fcaso)

# Modifying observation that are outside the location
d$fcaso[d$DPA_PARROQ == "050555"] <-0
d$fcaso[d$DPA_PARROQ == "180350"] <-0
d$fcaso[d$DPA_PARROQ == "060150"] <-0
d$fcaso[d$DPA_PARROQ == "060651"] <-0
d$fcaso[d$DPA_PARROQ == "030157"] <-0

# Variable optimal temperature
d <- d %>% 
  mutate(optimal = ifelse(is.na(opt3),0,1))

d$ftoptimal <- factor(d$optimal)
table(d$ftoptimal) #561 ok

table(is.na(d$pop))
d <- d %>% 
  mutate(pop2 = ifelse(is.na(pop),0,pop))
```

# Descriptive analysis
```{r setwd}
colnames(d)
# all variables 
chart.Correlation(d[,c(11:22)])

# Not correlated
chart.Correlation(d[,c(13:22,37)])
chart.Correlation(d[,c(16,19:20,28)])

cor(d[,c(11:22,25)])
```

```{r,}
# Model selection
# Backwards ----
m0 <- glm(d$fcaso ~ d$max + d$min + d$tdriest + d$pdriest + d$pwettest + d$pseason + d$pwarm +
            d$pcold + d$tseason + d$Prec + d$twettest + d$Temp, family = binomial(logit)) #AIC 758.5
summary(m0)
logistic.display(m0)

m1 <- glm(d$fcaso ~ d$max + d$min + d$tdriest + d$pdriest + d$pwettest + d$pseason + d$pwarm +
            d$pcold + d$tseason + d$Prec + d$twettest + d$Temp + d$pop2, family = binomial(logit)) #AIC 758.5
summary(m1)
logistic.display(m1)
```

```{r}
# Univariables models ----
m1 <- glm(d$fcaso ~ d$pwettest, family = binomial(logit))
summary(m1)
cbind(exp(coef(m1)), exp(confint(m1)))

m2 <- glm(d$fcaso ~ d$Prec, family = binomial(logit))
summary(m2)
cbind(exp(coef(m2)), exp(confint(m2)))

m3 <- glm(d$fcaso ~ d$pop2, family = binomial(logit))
summary(m3)
cbind(exp(coef(m3)), exp(confint(m3)))

m4 <- glm(d$fcaso ~ d$pdriest, family = binomial(logit))
summary(m4)
cbind(exp(coef(m4)), exp(confint(m4)))

m5 <- glm(d$fcaso ~ d$max, family = binomial(logit))
summary(m5)
cbind(exp(coef(m5)), exp(confint(m5)))

m6 <- glm(d$fcaso ~ d$min, family = binomial(logit))
summary(m6)
cbind(exp(coef(m6)), exp(confint(m6)))

m7 <- glm(d$fcaso ~ d$tseason, family = binomial(logit))
summary(m7)
cbind(exp(coef(m7)), exp(confint(m7)))
```


# Multivariable ----
```{r}
m1 <- glm(d$fcaso ~ d$pwettest + d$Prec + d$max + d$pop2 + d$min + d$pdriest +
            d$tseason, family = binomial(logit))
mr <- m1

m2 <- glm(d$fcaso ~ d$pwettest + d$pop2 + d$pdriest + d$max + d$min + d$tseason, family = binomial(logit)) #winner model
mr <- m2

m3 <- glm(d$fcaso ~ d$pwettest + d$pop2 + d$min + d$tseason , family = binomial(logit))
mr <- m3

anova(m2,m3, test = "Chisq")
```

```{r}
summary(mr)
logistic.display(mr)

d$m_prob <- predict.glm(mr, type="response")
d$predicted <- ifelse(d$m_prob < 0.5, 0, 1)
d$correct <- ifelse(d$predicted == d$fcaso, 1, 0)
table(d$correct)
table(d$correct)/length(d$fcaso)
table(d$correct[d$fcaso == 1]) #13
table(d$correct[d$fcaso == 0]) #874
hoslem.test(mr$y, fitted(mr)) #70% good fit
plotGLM(obs = mr$y, pred = mr$fitted.values) #r2:0.08, d2=0.10
AUC(model = mr) #0.73
library(car)
car::vif(mr)
car::outlierTest(mr)
car::influenceIndexPlot(mr, cex=0.01, main=NULL)

# Correlated observations that are important
#d <- d[-851,]
#d <- d[-611,]
```


# Predicted probability 
```{r}
#Individual probability of having the 
predicted.data <- data.frame(
  probabilidade.caso=mr$fitted.values,
  p.caso=mr$y)

predicted.data <- predicted.data[
  order(predicted.data$probabilidade.caso, decreasing=FALSE),]

predicted.data$rank <- 1:nrow(predicted.data)

head(predicted.data)

library(ggplot2)
ggplot(data=predicted.data, aes(x=rank, y=probabilidade.caso)) +
  geom_point(aes(x=rank, y=probabilidade.caso), stroke=0.05)+ 
  geom_point(aes(color=probabilidade.caso), alpha=0.9, shape=1, stroke=0.5) +
  theme(text = element_text(size = 10))+
  xlab("Predicted") +
  ylab("Case probability") +
  labs(color = "Pred.
Prob")+
  scale_color_viridis_c()+
  labs(tag = "b")+
  theme_linedraw()

boxplot(ec3_sf$Temp[!is.na(ec3_sf$inter)])

# Agregating t the map
ec3_sf$prob <- d$m_prob[match(ec3_sf$ID, d$ID)]
```

# plot parish with presence of BTV and points
# Fig Probability map ----
```{r}
pm <- ggplot() +
  geom_sf(data = ec3_sf, aes(fill = prob), linewidth = 0.00001) +
  scale_fill_continuous(low = "#fff7ec", high = "#7F0000", na.value ="gray99") +
  theme_minimal(base_size = 6) +
  theme(title = NULL,
        legend.key.width = unit(0.25, 'cm')) +
  labs(fill=("BTV\nParish\nProb"),
       x=NULL,
       y=NULL) +
  xlim(-81.1,-75.1)+
  ggsn::scalebar(ec3_sf, dist = 100, dist_unit = "km", 
                 transform = TRUE, model = "WGS84", st.size = 2, 
                 st.dist = 0.05, anchor = c(x = -76, y = -4.5), height = 0.02, border.size = 0.09) +
  ggsn::north(ec3_sf, symbol = 3) + 
  geom_point(data = points, aes(x = x, y = y, color = "BTV +"), 
  size = 0.05, alpha = 0.5, show.legend = TRUE) +
  scale_color_manual(values = c("BTV +" = "blue"), name = "Observed")

tiff(filename = "Fig.3.tiff", width=11.5, height=10,
       units="cm", res=1200,compression = "lzw", pointsize = 8)
pm
dev.off()
```

# Saving probdata
```{r}
colnames(d)
modelpredictions <- d[, c(1, 8, 6, 2, 19, 40, 20, 14,15, 13, 41  )]
head(modelpredictions)
write.csv(modelpredictions, file = "modelpredictions.csv")
```
